FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2018-06-05 ECOOP18/paper.tex
revision
marco's suggestions

\usepackage{xspace}
\usepackage{multicol}
\usepackage{microtype}%if unwanted, comment out or use option "draft"
%\usepackage[table,xcdraw]{xcolor} -- clash with preamble.tex
\usepackage{color}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{stmaryrd}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{url}
%\usepackage{pstricks,pst-node,pst-tree} -- clash with preamble.tex
\usepackage{bbm}
%\usepackage{pgf} -- clash with preamble.tex
\usepackage{multirow}
\usepackage{enumitem}

@@

% \newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
 \newcommand\yanlin[1]{\authornote{yanlin}{red}{#1}}
% \newcommand\marco[1]{\authornote{marco}{blue}{#1}}
% \newcommand\marcoT[1]{\authorText{blue}{#1}}
% \newcommand\haoyuan[1]{\authornote{haoyuan}{orange}{#1}}

\newcommand\bruno[1]{}
%\newcommand\yanlin[1]{}
\newcommand\marco[1]{}
\newcommand\haoyuan[1]{}

@@

\author{Yanlin Wang}
{The University of Hong Kong, China}
{ylwang@cs.hku.hk}
{}{}%mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
\author{Haoyuan Zhang}
{The University of Hong Kong, China}
{hyzhang@cs.hku.hk}
{}{}
\author{Bruno C. d. S. Oliveira}
{The University of Hong Kong, China}
{bruno@cs.hku.hk}
{}{}
\author{Marco Servetto}
{Victoria University of Wellington, New Zealand}
{marco.servetto@ecs.vuw.ac.nz}
{}{}

@@

\Copyright{John Q. Public and Joan R. Public}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\subjclass{Dummy classification}% mandatory: Please choose ACM 2012 classifications from https://www.acm.org/publications/class-2012 or https://dl.acm.org/ccs/ccs_flat.cfm . E.g., cite as "General and reference $\rightarrow$ General literature" or \ccsdesc[100]{General and reference~General literature}.

\keywords{Dummy keyword}%mandatory

@@

\acknowledgements{I want to thank \dots}%optional

>>>>

\usepackage{xspace}
\usepackage{multicol}
\usepackage{microtype}%if unwanted, comment out or use option "draft"
%\usepackage[table,xcdraw]{xcolor} -- clash with preamble.tex
\usepackage{color}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{stmaryrd}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{url}
%\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
%\usepackage[hyphens]{url}
%\usepackage{pstricks,pst-node,pst-tree} -- clash with preamble.tex
\usepackage{bbm}
%\usepackage{pgf} -- clash with preamble.tex
\usepackage{multirow}
\usepackage{enumitem}

@@

\newcommand\bruno[1]{\authornote{bruno}{blue}{#1}}
 \newcommand\yanlin[1]{\authornote{yanlin}{red}{#1}}
% \newcommand\marco[1]{\authornote{marco}{blue}{#1}}
% \newcommand\marcoT[1]{\authorText{blue}{#1}}
% \newcommand\haoyuan[1]{\authornote{haoyuan}{orange}{#1}}

%\newcommand\bruno[1]{}
%\newcommand\yanlin[1]{}
\newcommand\marco[1]{}
\newcommand\haoyuan[1]{}

@@

\author{Yanlin Wang$^1$}
{The University of Hong Kong, China}
{ylwang@cs.hku.hk}
{}{}%mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
\author{Haoyuan Zhang$^1$}
{The University of Hong Kong, China}
{hyzhang@cs.hku.hk}
{}{}
\author{Bruno C. d. S. Oliveira}
{The University of Hong Kong, China}
{bruno@cs.hku.hk}
{}{Funded by Hong Kong Research Grant Council projects number 17210617 and 17258816}
\author{Marco Servetto}
{Victoria University of Wellington, New Zealand}
{marco.servetto@ecs.vuw.ac.nz}
{}{}

@@

\Copyright{Yanlin Wang, Haoyuan Zhang, Bruno C. d. S. Oliveira and Marco Servetto}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\subjclass{Software and its engineering $\rightarrow$ Object oriented languages}% mandatory: Please choose ACM 2012 classifications from https://www.acm.org/publications/class-2012 or https://dl.acm.org/ccs/ccs_flat.cfm . E.g., cite as "General and reference $\rightarrow$ General literature" or \ccsdesc[100]{General and reference~General literature}.

\keywords{multiple inheritance; hierarchical dispatching; OOP; language design}%mandatory

@@

\acknowledgements{We thank the anonymous reviewers for their valuable comments.}%optional
